Programming Assignment 2

### 2015-04-01 paper.tex
Added sections and subsections as per Project Report specs

%I don't know what sections we need! Add and remove as you see fit
\section{Overview}

\section{Program Description}

>>>>

%Feel free to remove the 'description' text i placed (e.g. "Our hopfield network was terrific! Type stuff here")
\section{Overview}

\section{Hopfield Autoassociative Memory Network}
Our hopfield network was terrific! Type stuff here

\subsection{Image Encoding}
The image encoding... blah blah. Type here

\subsection{Performance}
Here is where we need to talk about how long it took and how good it was. We
also might want to mention the size limitations this introduced!

\subsection{Sensitivity}
This section is about how badly noise and the size disrupted our accuracy

\subsection{Comments}
It says "your own observation and conclusions about the experiment."
I'm thinking we talk generally about how it did (like a conclusion) and how
what we did ended up working.

\section{Hamming-Max Network}

\subsection{Image Encoding}
The image encoding... blah blah. Type here

\subsection{Performance}
Here is where we need to talk about how long it took and how good it was. We
also might want to mention the size limitations this introduced!

\subsection{Sensitivity}
This section is about how badly noise and the size disrupted our accuracy

\subsection{Comments}
It says "your own observation and conclusions about the experiment."
I'm thinking we talk generally about how it did (like a conclusion) and how
what we did ended up working.

\section{Bidirection Associative Memory (BAM)}

\subsection{Image Encoding}
The image encoding... blah blah. Type here

\subsection{Performance}
Here is where we need to talk about how long it took and how good it was. We
also might want to mention the size limitations this introduced!

\subsection{Sensitivity}
This section is about how badly noise and the size disrupted our accuracy

\subsection{Comments}
It says "your own observation and conclusions about the experiment."
I'm thinking we talk generally about how it did (like a conclusion) and how
what we did ended up working.

\section{LVQ}

\subsection{Image Encoding}
The image encoding... blah blah. Type here

\subsection{Performance}
Here is where we need to talk about how long it took and how good it was. We
also might want to mention the size limitations this introduced!

\subsection{Sensitivity}
This section is about how badly noise and the size disrupted our accuracy

\subsection{Comments}
It says "your own observation and conclusions about the experiment."
I'm thinking we talk generally about how it did (like a conclusion) and how
what we did ended up working.
